MERF: Morphology-based Entity and Relational Entity Extraction Framework for Arabic \\ ~~ \\ Response to Major Revision

### 2018-04-20 tex/merf/TALMajor/answer/Reviewer3.comments.tex
left with 3.3 3.20 3.24 3.27 and 4.3

\done{
  DONE: Ameen please find where you fixed this and say it here. 
}

@@

\answer{
We clarify the definition of MRE in the paper. 
}

\itodo{
  Clarify the definition. 
}

@@

\answer{
We rewrote both sections... 
}

\itodo{
  Figure our something to do/say.
}

@@

\answer{
We provide running examples with the definitions....
}
\itodo{
  Color them and say where they are. 
}

@@

\done{
  Add that to the Results.\\
  Added the above explanation in the Results section, needs to be checked.
}

@@

\done{
  highlight the changes and refer to them please.\\
  We use R first to denote the set of user-defined relations.
  Then, we use it to denote the set of MBF tags which is contradicting.
  I got rid of the first case as we don't need it.
}

@@

\answer{
  We used XXX data structures... 
}

\itodo{
  Ameen: JSON add that as a paragraph in the methodology section. 
}

@@

\item \label{Review.3.24}
Also, comparison with previous work done by (Zaraket ) 
in different vesion seems like comparing with your previous work 
only and not with others. 
It would be nice to compare others work too because user 
interface could be introduced in different view.

@@

\item \label{Review.3.24}
What is the data size of your evaluation? 
I couldn't find how presion and recal was counted. 
you mentioned books but did you covered all the text in those 
books ? and how long was it? you can define it in term of 
number of relation extracted , tags added, expesion processed, 
sentences,..etc

\answer{
  We include more information about the data and 
  the evaluation process... 
}

\itodo{
  Answer.. 
}

\item \label{Review.3.24}
7- At section Discussion, I strongly urge you to discuss 
WHY the precision and recall have these values.

@@

\item \label{Review.3.25}
Clarity:  
It was not very clear how the work was done 
``Methodology part''. 
Section 4 ``MERF'' please add ``Methedology''.

@@

\item \label{Review.3.25}
Having ``Existing annotation and entity extraction tools'' 
under unspecified section is misleading the reader. 
unnumbered subsections was misleading me as a reader.

\answer{
  Fixed. CLS file was not compatible with arabtex package. 
}

\item \label{Review.3.25}
table 1 at page 7 while referring to it only at page 9. 
I think it needs to be closer to where it was mentioned in the text.

@@

\done{
  Done: Make sure this is moved. 
}

\item \label{Review.3.25}
``MERF regular expressions support operators such as concatenation, zero or one, zero or more, one or more, up to $M$” what is M? 
it could be for example 0<=M<=|chunk|

@@

\item \label{Review.3.25}
Correctness: 
1- in the abstract, the sentence ``These techniques and 
tools require expertise in linguistics and programming and 
lack support of Arabic morphological analysis which is key to 
process Arabic text''
gives the meaning that ``it require lack support'' so I think it 
needs to be reformulated

@@

\item \label{Review.3.25}
2-``defines tag types and''.// unify the font here and 
many other places in the paper. 
for example look at words(,correct,commercial)

\answer{
  We use italics to emphasize important 
  concepts that we introduce for the first time. 
  We reduced the use of emphasize in the paper. 
}

\item \label{Review.3.25}
Originality:  
This work will contribute in facilitating Arabic corpus 
annotation, if it was made available for other researchers in 
the field to access and use it, although there is no 
referencing to where it can be accessed. 
this is an improvement of a per-existing work ``MATAr: Morphology-based Tagger for Arabic''

>>>>

@@

\answer{
  We modified the definition. We also 
  followed the MRE definition with a running illustrating example.
}

@@

\answer{
  We provided a running example across both sections and rewrote parts of the sections. 
}

@@

\answer{
We provide running examples with the definitions....
}

@@

@@

@@

\answer{
  We included descriptions of the storage format 
  in the Methodology Section~\ref{sec:methodology}. 
}

@@

\item \label{Review.3.25}
Also, comparison with previous work done by (Zaraket ) 
in different version seems like comparing with your previous work 
only and not with others. 
It would be nice to compare others work too because user 
interface could be introduced in different view.

@@

\item \label{Review.3.26}
What is the data size of your evaluation? 
I couldn't find how precision and recall was counted. 
you mentioned books but did you covered all the text in those 
books ? and how long was it? you can define it in term of 
number of relation extracted , tags added, expression processed, 
sentences,..etc

\answer{
  We include more information about the data and 
  the evaluation process.
  We include the size of the annotated data sets that 
  we used for accuracy evaluation in Table~\ref{tab:results}. 
  We discuss how the golden reference was constructed. 
  We also discuss the workload of the research assistant who built
  the task specific case studies. 
}

\item \label{Review.3.27}
7- At section Discussion, I strongly urge you to discuss 
WHY the precision and recall have these values.

@@

\item \label{Review.3.28}
Clarity:  
It was not very clear how the work was done 
``Methodology part''. 
Section 4 ``MERF'' please add ``Methedology''.

@@

\item \label{Review.3.29}
Having ``Existing annotation and entity extraction tools'' 
under unspecified section is misleading the reader. 
unnumbered subsections was misleading me as a reader.

\answer{
  We fixed the non-numbered subsections.
  We removed Subsection ``Existing annotation and entity extraction tools''
  as requested in \ref{Review.3.9}.
}

\item \label{Review.3.30}
table 1 at page 7 while referring to it only at page 9. 
I think it needs to be closer to where it was mentioned in the text.

@@

\item \label{Review.3.31}
``MERF regular expressions support operators such as concatenation, zero or one, zero or more, one or more, up to $M$” what is M? 
it could be for example 0<=M<=|chunk|

@@

\item \label{Review.3.32}
Correctness: 
1- in the abstract, the sentence ``These techniques and 
tools require expertise in linguistics and programming and 
lack support of Arabic morphological analysis which is key to 
process Arabic text''
gives the meaning that ``it require lack support'' so I think it 
needs to be reformulated

@@

\item \label{Review.3.33}
2-``defines tag types and''.// unify the font here and 
many other places in the paper. 
for example look at words(,correct,commercial)

\answer{
  We used italics to emphasize important 
  concepts that we introduce for the first time. 
  We reduced the use of emphasid text in the paper. 
}

\item \label{Review.3.34}
Originality:  
This work will contribute in facilitating Arabic corpus 
annotation, if it was made available for other researchers in 
the field to access and use it, although there is no 
referencing to where it can be accessed. 
this is an improvement of a per-existing work ``MATAr: Morphology-based Tagger for Arabic''

### 2018-04-20 tex/merf/TALMajor/answer/Reviewer4.comments.tex
left with 3.3 3.20 3.24 3.27 and 4.3

\done{
  Discussion of the code actions is pending...
}

\item \label{Review.4.1} 
Correctness :  
- $Syn^k$ introduces a lot of noise especially if $k$ is large.

@@

\done{
  Done: Use the same answer for Reviewer 3, and say why you used 7. 
}

\item \label{Review.4.1} 
In the results section, there is no standard evaluation. 
The evaluation is based on comparisons with non-standard 
task-specific tools. 
Also, the reported precision and recall are very sensitive 
to the quality of the annotator!

@@

\itodo{
Say something about clarifying the evaluation process. 
}

>>>>

\item \label{Review.4.2} 
Correctness :  
- $Syn^k$ introduces a lot of noise especially if $k$ is large.

@@

\item \label{Review.4.3} 
In the results section, there is no standard evaluation. 
The evaluation is based on comparisons with non-standard 
task-specific tools. 
Also, the reported precision and recall are very sensitive 
to the quality of the annotator!

@@
